Gammapy: A Python package for gamma-ray astronomy

### 2023-03-03 src/ms-review.tex
Fix #108

\abstract
	{
		Traditionally, TeV-\gammaray astronomy has been conducted
		by experiments employing proprietary data and analysis software.
		However, the next generation of \gammaray instruments,
		such as the the Cherenkov Telescope Array, will be operated as open observatories.
		Alongside the data, they will make software tools for their analysis available to the community.
    This necessity prompted the development of open, high-level astronomy software customised for high energy astrophysics.
	}
	{
		In this article, we present \gammapy, an open-source Python package for the analysis of astronomical \gammaray data,
		and illustrate the functionalities of its first long-term-support release, version 1.0.
		Built on the modern Python scientific ecosystem, \gammapy provides a uniform platform for reducing and
		modelling data from different \gammaray instruments for many analysis scenarios.
    \gammapy complies with several well-established data conventions in high-energy astrophysics, providing serialised data products that
		are interoperable with other software packages.
	}
	{
		Starting from event list and instrument response functions,
		\gammapy provides the functionalities for reducing data binned in energy and sky coordinates.
		To handle the residual hadronic background, several techniques for background estimation
		are implemented in the package.
		After the data are binned, the flux and morphology of one or more \gammaray sources can be estimated
		using Poisson maximum likelihood fitting
		and assuming a variety of spectral, temporal and spatial models.
		Estimation of flux points, likelihood profiles and light curves is also supported.
	}
	{
		After describing the structure of the package, we show the capabilities of \gammapy
		in multiple traditional and novel \gammaray analysis scenarios using public data
		such as spectral and spectro-morphological modelling and estimations of a spectral energy
		distribution and a light curve.
		Its flexibility and its power are displayed in a final multi-instrument example,
		where datasets from different instruments, at different stages of data reduction,
		are simultaneously fitted with an astrophysical flux model.
	}{}

@@

\textit{Imaging Atmospheric Cherenkov Telescopes (IACT)} obtain images of the atmospheric showers
by detecting the Cherenkov radiation emitted by the cascading charged particles and
use these images to reconstruct the properties of the incident particle.
Those instruments have a limited field of view (FoV) and duty cycle, but
good energy and angular resolution.

>>>>

\abstract
	{
		Traditionally, TeV-\gammaray astronomy has been conducted
		by experiments employing proprietary data and analysis software.
		However, the next generation of \gammaray instruments,
		such as the the Cherenkov Telescope Array, will be operated as open observatories.
		Alongside the data, they will also make associated software tools available to a wider community.
    This necessity prompted the development of open, high-level astronomy software customised for high energy astrophysics.
	}
	{
		In this article, we present \gammapy, an open-source Python package for the analysis of astronomical \gammaray data,
		and illustrate the functionalities of its first long-term-support release, version 1.0.
		Built on the modern Python scientific ecosystem, \gammapy provides a uniform platform for reducing and
		modelling data from different \gammaray instruments for many analysis scenarios.
    \gammapy complies with several well-established data conventions in high-energy astrophysics, providing serialised data products that
		are interoperable with other software packages.
	}
	{
		Starting from event list and instrument response functions,
		\gammapy provides the functionalities for reducing data binned in energy and sky coordinates.
		To handle the residual hadronic background, several techniques for background estimation
		are implemented in the package.
		After the data are binned, the flux and morphology of one or more \gammaray sources can be estimated
		using Poisson maximum likelihood fitting
		and assuming a variety of spectral, temporal and spatial models.
		Estimation of flux points, likelihood profiles and light curves is also supported.
	}
	{
		After describing the structure of the package, we show the capabilities of \gammapy
		in multiple traditional and novel \gammaray analysis scenarios using public data
		such as spectral and spectro-morphological modelling and estimations of a spectral energy
		distribution and a light curve.
		Its flexibility and its power are displayed in a final multi-instrument example,
		where datasets from different instruments, at different stages of data reduction,
		are simultaneously fitted with an astrophysical flux model.
	}{}

@@

\textit{Imaging Atmospheric Cherenkov Telescopes (IACTs)} obtain images of the atmospheric showers
by detecting the Cherenkov radiation emitted by the cascading charged particles and
use these images to reconstruct the properties of the incident particle.
Those instruments have a limited field of view (FoV) and duty cycle, but
good energy and angular resolution.
